\documentclass[8pt]{article} 

\usepackage[utf8]{inputenc}
\usepackage[top=2cm, bottom=2.5cm, left=3cm, right=3cm]{geometry}

\title{Unemployment}
\author{LUKWAGO HASSAN NASSIL\\
16/U/6666/EVE\\
216005795
}
\date{} 

\begin{document}
\maketitle

\section*{Unemployment}

Unemployment refers to the situation where people in a particular locality can not find jobs either with limited skills or with skills but no jobs for the particular skill.

\section{Main Reason of Unemployment}
Global economic crisis which exists: Of all the many causes of unemployment which exist, the main causes of unemployment   can be pointed to the global economic crisis which exists at the moment and has existed for a while.
This economic crisis has effected in a very negative manner, the trade between countries. Countries which were previously rather rich have not been able to withstand the economic crisis.
In order to avoid any kinds of major losses, companies too have begun to decrease the production of their goods, since not many individuals are willing to invest a lot of money in purchasing things.


\section{The Causes of Unemployment}


1. The large number of technological advancements:\\
It is very needless to say that today we live in an age of technology. Previously companies required a lot of labor in order to perform tasks for them.
However nowadays, computers and various other machines can perform even the most complex of tasks in a matter of minutes. In addition to that, some years ago, even sending one message or reply took so much of time.
Nowadays with the help of the internet, things are done in the matter of minutes and it is for this reason that so many people are no longer required to do tasks which required manual labor and intellectual ability. This is one of the reason of unemployment.\\
2. Jobs have become increasingly specialized:\\
Big companies provide their employees with a large number of benefits and facilities. It is for this reason that when looking for employees, they have a large number of specifications.
Unless a person fulfills all the requirements, he or she will not even be considered for the position at hand. Since job descriptions have become so very specific and particular, people are finding it very tough to even get an interview.
At such a point in time there is little which can be done, because companies will not be willing to take on board those who are not exactly perfect for the job.\\
3. Companies prefer hiring few people on board:\\
Previously top companies hired a large number of people so as to ensure that all the jobs get done in a proper manner, within the stipulated deadline.
However nowadays, companies prefer to hire as few people as possible on board. This is so that they do not have to spend too much money on salaries and secondly so that their trade secrets do not go out. They are only willing to hire those people who they trust and are entirely sure of.
Many bosses believe that hiring 5 competent people on board is better than having 20 average people. Offices only hire rockstar employees who are all rounders and are capable of excellent work at all times.\\
4. People voluntarily choose to remain unemployed:\\
There are many individuals out there who are very specific when it comes to choosing jobs, simply because they do not work in a company which they would not like to mention on their CV, in the future.
On the other end of the spectrum, there are those individuals who are willing to take up any job as long as they are getting a salary and job.
The first kind of people prefer to wait for the right job to come along and that is why they end up being unemployed. They too want to be employed but they are unwilling to take up simply any and every job which happens to come their way.\\
5. A higher literacy rate among men and women:\\
Till a few years ago, the literacy rate the world over was not very high at all. However nowadays more and more people from even the rural regions are coming forward in order to receive an education.
In addition to this even women are being encouraged to come forward and study so that their future is bright and promising. It is very sad indeed that because so many people are educated, the number of jobs are falling short and that is why there is so much of unemployment especially in big cities.
Once people are well educated, chances are that they will be unwilling to accept a job which is not worthy of their intellect.\\
6. The issue of the immobility of the work force:\\
In certain places job opportunities are more than others. Some places are just not developed enough to provide jobs to a large number of people.
The immobility of the work or labor force is one major reason for unemployment as well. For various reasons certain able people are simply unwilling to migrate from one location to the next. Rather than taking the plunge, they prefer to remain close to home and families as well.
Doing this is something which is not very wise simply because if you realize that your current location does not hold much potential for you and your career, you must be willing to relocate.\\


\end{document}
